Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-20 talk_ucl_cdt_200622/introduction.tex
drop wall
use the isotope package to typeset nuclear reactions

\begin{frame}
	\frametitle{Problem Description}
	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
	\begin{center}
	$^1_0n + ^6_3Li \rightarrow ^3_1H + ^4_2He$ \hspace{20pt} $^1_0n + ^7_3Li \rightarrow ^3_1H + ^4_2He + ^1_0n$
	\end{center}
	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline

@@

			\begin{itemize}
				\item
					Regression performance: mean absolute error, $\sigma$ of
					error, $R^2$, $R^2_\text{adj.}$
				\item
					Computational complexity:
					wall training \& prediction time / sample.
			\end{itemize}

>>>>

\begin{frame}
	\frametitle{Problem Description}
	Tritium breeding blankets convert neutron radiation from the fusion plasma into a steady supply of tritium fuel.
	\begin{align*}
		\isotope[1][0]{n} + \isotope[6][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He}
		\qquad\qquad
		\isotope[1][0]{n} + \isotope[7][3]{Li} \rightarrow \isotope[3][1]{H} +
		\isotope[4][2]{He} + \isotope[1][0]{n}
	\end{align*}
	However, the tritium breeding ratio (TBR) depends on numerous geometric and material parameters.\newline

@@

			\begin{itemize}
				\item
					Regression performance: mean absolute error, $\sigma$ of
					error, $R^2$, $R^2_\text{adj.}$
				\item
					Computational complexity:
					training \& prediction time / sample.
			\end{itemize}
